Triangulating iconicity: Coding analysis

### 2024-04-27 paper_02_main_analyses.Rmd
+csv version of full ratings data
anon

---
title: "Triangulating iconicity: Coding analysis"
author: "Mark Dingemanse, Stella Punselie, Bonnie McLean"
date: "Updated `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Triangulating iconicity: Coding analysis"
author: "[anonymised for review]"
date: "Updated `r format(Sys.Date())`"
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

write.csv(d.ratings.full, file="data/ideophones_rated.csv")
